The value of intermediation

### 2022-09-13 src/presentation/presentation.qmd
Add first set of videos to the presentation

---
title: "The value of intermediation"
author: "Martin Stancsics"
format: revealjs
bibliography: references.bib
---

@@

@@

::: {.column width="40%"}
contents...
:::

::: {.column width="60%"}
contents...
:::

>>>>

---
title: "The value of intermediation"
author: "Martin Stancsics"
format:
    revealjs:
        embed-resources: true
        transition: fade
bibliography: references.bib
---

@@

An example game in coalitional form

::: {.column width="50%"}
Imagine a game with three players:

 - A wholesale producer: $P$
 - Two downstream resellers: $A_1, A_2$

:::

::: {.column width="10%"}
:::

::: {.column width="40%"}
And the following achievable profits:

Coalition | Profits
----------|---------
$\{P\},  \{A_i\}$     |  0
$\{A_1, A_2\}$  | 0  
$\{P, A_i\}$  | 2 
$\{P, A_1, A_2\}$  | 3
:::

@@

::: {.column width="50%"}
::: {.r-stack}

::: {.fragment}
   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/draw_objects.mp4" />
:::
::: {.fragment}
   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_P12.mp4" />
:::
::: {.fragment}
   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_P21.mp4" />
:::
::: {.fragment}
   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_2P1.mp4" />
:::
::: {.fragment}
   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_1P2.mp4" />
:::
::: {.fragment}
   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_12P.mp4" />
:::
::: {.fragment}
   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_21P.mp4" />
:::
::: {.fragment}
   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/final.mp4" />
:::

:::
:::

::: {.column width="10%"}
:::

::: {.column width="40%"}
And the following achievable profits:

Coalition | Profits
----------|---------
$\{P\},  \{A_i\}$     |  0
$\{A_1, A_2\}$  | 0
$\{P, A_i\}$  | 2 
$\{P, A_1, A_2\}$  | 3
:::
